---
title: "Reproducible Research: Peer Assignment 1"
author: "Jong-dae Kim"
date: '2017 6 12 '
output: 
  html_document: 
    fig_caption: yes
    keep_md: yes
    toc: yes
---
This is the R Markdown for the Preer Assignment 1 of "Reproducible Research".
I am Jong-dae Kim in South Korea.

Glad to meet you and Thank you for your reviewing.

Let get start.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages
```{r load packages,  echo = TRUE , results='hide'}
library(dplyr)
library(ggplot2)
```



## Loading the data
```{r load the data,   echo = TRUE}
activity <- read.csv("activity.csv")
```



## What is mean total number of steps taken per day?
```{r mean_total_number,  echo = TRUE}
activity_date <- group_by(activity, date) %>%
     summarize(total_steps = sum(steps))
hist(as.numeric(activity_date$total_steps ),
    xlab = "Number of steps",
    ylab = "Number of days",
    main = "Histogram of Total number of steps taken per day")
summary(activity_date$total_steps)
```




## What is the average daily activity pattern?
1. Time series plot
```{r  average_daily_activity,  echo = TRUE}
activity_interval <- group_by(activity, interval) %>% summarize(mean_steps = mean(steps, na.rm=TRUE))
ggplot(activity_interval, aes(x=interval, y=mean_steps)) + geom_point() +
    labs(x = "5-Minute Interval", y = "Mean of Steps", 
        title = "Time series plot of mean of steps taken per 5-minute interval")
with(activity_interval, plot(interval, mean_steps, type = "l", 
    xlab = "5-Minute Interval",ylab = "Mean of Steps",
    main = "Time series plot of mean of steps taken per 5-minute interval") )
```





2. 5-minute interval, contains the maximum numbers of steps
```{r maximum numbers of steps,  echo = TRUE}
max_interval <- which.max(activity_interval$mean_steps)
activity_interval[max_interval,]
```




## Imputing missing values

1. Calculate and report the total number of missing values in the dataset 
```{r Imputing missing values,  echo = TRUE}
sum(is.na(activity$date))
sum(is.na(activity$interval))
sum(is.na(activity$steps))
```

2. Create a new dataset with the missing data filled in(the mean for that 5-minute interval)
```{r,  echo = TRUE}
new <- activity
for (i in 1:17568){
    if (is.na(new[i,1]) == TRUE) {
        new[i,1] <- activity_interval[activity_interval$interval==new[i,3], 2]
    }
}
   
sum(is.na(new$steps))

```

3. Make a histogram of the total number of steps taken each day 

```{r imputing_missingd_ata,  echo = TRUE}
new_date <- group_by(new, date) %>%
    summarize(total_steps = sum(steps))
hist(new_date$total_steps,     
    xlab = "Number of steps",
    ylab = "Number of days",
    main = "Histogram of Total number of steps taken per day \n 
    after imputing missing data")
```




4. Report the mean and median total number of steps taken per day. 
```{r,  echo = TRUE}
summary(new_date$total_steps)
```

There is a little difference between the former estimates and the latter estimates
There is a little impact of imputing missing data on the estimates of the total daily number of steps.

## Are there differences in activity patterns between weekdays and weekends?

```{r differences_in_activity,  echo = TRUE}

wday <- unclass(strptime(new$date, "%Y-%m-%d"))$wday
new <- cbind(new, wday)
new[new$wday == 0 | new$wday == 6, 4] <- "weekends"
new[!(new$wday == "weekends"), 4] <- "weekdays"
new_interval <- group_by(new, interval, wday) %>% summarise(avr_steps = sum(steps))
ggplot(new_interval, aes(interval, avr_steps, color = wday)) + geom_line() +
    facet_grid(.~wday)

```





There was more steps on weekends than on weekdays, especially in the morning.







